My title

### 2023-03-12 outputs/paper/paper.qmd
- Added a potential summary statistics table to the end of "03-rough_work" script - Copied the same potential summary statistics table to the Data section of the "paper" Quarto doc

install.packages("kableExtra")
install.packages("tidyverse")

library(kableExtra)
library(tidyverse)
```

@@

@@

```{r}
## Graph Level of Happiness VS. Internet Hours##
mean_happy<- cleaned_2016gss_data %>%
  select(`Level of Happiness`,`Weekly Total of Internet Use (Hours)`) %>%
  group_by(`Level of Happiness`)%>%
  summarise(Mean_total = mean(`Weekly Total of Internet Use (Hours)` , na.rm=TRUE) )%>%
  pivot_wider(names_from = "Level of Happiness", values_from = c("Mean_total"))

@@

>>>>

install.packages("kableExtra")
install.packages("tidyverse")
install.packages("lessR")
install.packages("tidyr")
install.packages("reshape2")
install.packages("knitr")
install.packages("haven")
install.packages("vtable")

library(kableExtra)
library(tidyverse)
library(lessR)
library(tidyr)
library(reshape2)
library(knitr)
library(haven)
library(vtable)
```

@@

```{r}
# Summary statistics of our GSS data 
summ_gss <- cleaned_2016gss_data %>% 
  select(`Age.Group`, `Sex`, `Race`, `Personal.Income`, `Total.Family.Income`, 
         `Highest.Education.Obtained`, `Number.of.Children`, `Marital.Status`,
         `Level.of.Happiness`, `Weekly.Total.of.Internet.Use..Hours.`)
# sumtable(summ_gss,  title = "Summary Statistics of Our Variables", out = "kable")
## the final line doesn't work for some reason and i'm mad
```

@@

```{r}
#| label: fig-happyandinternet
#| fig-cap: Weekly Total of Internet Use by Level of Happiness
#| echo: false
## Graph Level of Happiness VS. Internet Hours##
mean_happy<- cleaned_2016gss_data %>%
  select(`Level of Happiness`,`Weekly Total of Internet Use (Hours)`) %>%
  group_by(`Level of Happiness`)%>%
  summarise(Mean_total = mean(`Weekly Total of Internet Use (Hours)` , na.rm=TRUE) )%>%
  pivot_wider(names_from = "Level of Happiness", values_from = c("Mean_total"))

@@

```{r}
#| label: fig-educandinternet
#| fig-cap: Weekly Total of Internet Use by Highest Education Obtained
#| echo: false
## Highest Education Obtained VS. Internet Hours ##
mean_edu<- cleaned_2016gss_data %>%
  select(`Highest Education Obtained`,`Weekly Total of Internet Use (Hours)`) %>%
  group_by(`Highest Education Obtained`)%>%
  summarise(Mean_total = mean(`Weekly Total of Internet Use (Hours)` , na.rm=TRUE) )%>%
  pivot_wider(names_from = "Highest Education Obtained", values_from = c("Mean_total"))

## mutate from wide to long 
mean_edu <- melt(mean_edu)  #the function melt reshapes it from wide to long
mean_edu <- mean_edu[-6,]  # delete NA row

# save mean data
write_csv(mean_edu, "outputs/data/mean_edu.csv")

# use tidyverse-style code to pivot and summarise the data 
mean_edu |> ggplot(aes(x = variable, y = value)) + 
  geom_point() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 12)) +
  labs(
    x = "Highest Education Obtained",
    y = "Internet Usage Hours"
  )
```
